Docker {{< fa brands docker >}}

### 2023-08-11 _repro.qmd
Built site for gh-pages

1. Download and install Docker
2. Pull the [gongcastro/cognate-beginnings image](https://hub.docker.com/r/gongcastro/cognate-beginnings). Two ways of doing this:
    a) Using the Docker UI: go the the "Images" tab, click on "Search images to run", search for "gongcastro/cognate-beginnings", and click "Pull".
    b) Using the Docker CLI: open your console/terminal/command prompt, and run:
    ```bash 
    docker pull gongcastro/cognate-beginnings
    ```
3. Run the image in a Docker container. Two ways of doing this:
    a) Using the Docker UI: in the "Images" tab, look for the `gongcastro/cognate-beginnings` image and click "Run".
    b) Using the Docker CLI:
    ```bash 
    docker run --rm -ti -e ROOT=true -e PASSWORD=rstudio -p 8787:8787 --name rstudio gongcastro/cognate-beginnings:latest
    ```

>>>>

1. Download and install Docker ([Windows](https://docs.docker.com/desktop/install/windows-install/), [Mac](https://docs.docker.com/desktop/install/mac-install/), [Linux](https://docs.docker.com/desktop/install/linux-install/))
2. Pull the [gongcastro/cognate-beginnings image](https://hub.docker.com/r/gongcastro/cognate-beginnings). Two ways of doing this:
    a) Using the Docker Desktop app: go the "Images" tab, click on "Search images to run", search for "gongcastro/cognate-beginnings", and click "Pull".
    ```bash 
    docker pull gongcastro/cognate-beginnings
    ```
    b) Using the Docker CLI: open your console/terminal/command prompt, and run:

3. Run the image in a Docker container. Two ways of doing this:
    a) Using the Docker UI: in the "Images" tab, look for the `gongcastro/cognate-beginnings` image and click "Run".
    b) Using the Docker CLI:
    ```bash 
    docker run --rm -ti -e ROOT=true -e PASSWORD=rstudio -p 8787:8787 --name rstudio gongcastro/cognate-beginnings:latest
    ```
